Improving the Usability of Remote Access to Sensitive Data

### 2014-07-19 ccsw14/paper.tex
Added threat model + security guarantees section

\title{Securing Remote Access to Sensitive Data}

@@

\section{Related Work}
Donec ornare iaculis nisl, sit amet luctus metus varius ac. Nam eget tincidunt
magna. Sed convallis pulvinar eros sed consequat. Pellentesque posuere orci id
leo molestie, ac rutrum dolor pretium. In orci lectus, sollicitudin nec tellus
non, dictum egestas ante. Ut venenatis libero risus, sed auctor lorem
scelerisque at. Suspendisse porta elementum magna, id ornare erat placerat at.
In tincidunt dolor porta justo rhoncus elementum.

\section{Background}
Nullam viverra turpis nisi, id consequat urna pulvinar eu. Praesent ac pulvinar
nisl. Integer vel est a libero molestie mollis id vel tortor. Morbi ante odio,
cursus et volutpat a, pharetra at erat. Pellentesque habitant morbi tristique
senectus et netus et malesuada fames ac turpis egestas. Curabitur dignissim,
purus at auctor laoreet, magna mi auctor nulla, et mollis eros nisl vel lectus.
Integer bibendum purus ac adipiscing bibendum.

\section{Design and Implementation}
Suspendisse potenti. Donec ornare metus sem, vel semper arcu fermentum in. Nunc
vehicula eros turpis, ut rhoncus nunc sodales pulvinar. Duis sed est interdum,
semper mi a, cursus sapien. Nulla elementum congue purus, eu faucibus nibh
congue et. Ut diam metus, euismod ac quam in, gravida dictum turpis. Vivamus
hendrerit facilisis tempor. Curabitur hendrerit orci ac libero vestibulum, sit
amet dictum enim viverra. Nulla rutrum dolor ligula, nec rutrum massa suscipit
volutpat. Aliquam id mi at velit aliquet imperdiet at nec mi. Integer in massa
nec augue dapibus ullamcorper. Aliquam nec sollicitudin elit.

\section{Discussion and Future Work}
In eu gravida ligula, sit amet tincidunt nisi. Interdum et malesuada fames ac
ante ipsum primis in faucibus.  Vestibulum venenatis non sem vitae hendrerit.
Cras accumsan vel mauris ut vestibulum. Pellentesque auctor quam ut nisl
commodo malesuada. Phasellus adipiscing placerat tortor, in convallis massa
cursus eu. Vestibulum ullamcorper lorem vel nunc dictum, elementum pretium
nulla tincidunt.

>>>>

\title{Improving the Usability of Remote Access to Sensitive Data}

@@

\section{Related Work}

\section{Design}

We now discuss the design of the Data Capsules system.  This includes the
functional requirements for the two modes of operation and a discussion of how
the system avoids various channels for leaking data.

\subsection{Security Guarantees and Threat Model}

The goal of the Data Capsules system is to provide a usable environment for data
analysis that also provides a reasonably strong (as we elaborate on below)
guarantee of data privacy from parties other than the end user to whom a VM
belongs.  Data Capsules is not designed to provide any protection to the
integrity of sensitive data.  This is assumed trivial, as the sensitive data is
presumably unchanging, so that making it read-only and creating appropriate
backup copies should be a sufficient practice to ensure the data's integrity.

The end user is assumed to be largely trustworthy, since they have presumably
undergone a vetting process before receiving permission to analyze the sensitive
data.  However, we do recognize the possibility that others could gain temporary
access to a VM, for example by using a researcher's machine after they
momentarily step away.  If the device through which an end user accesses their
remote VM becomes compromised, this could also open the possibility of long-term
access to the VM.  While the current implementation does not fully address
either of these possibilities, we discuss the paths we are investigating in
Section \ref{sec:Discussion}.

Within a user's VM, we make no assumptions about the software environment and
treat everything as untrusted, down to the operating system.  Data Capsules is
designed so that malicious software may succeed in accessing the sensitive data,
but will be incapable of reliably exfiltrating it from the virtual machine.
Under this design, we consider the following potential channels for data leaks:

\textbf{Storage Channels} It should not be possible for data that is produced
as the result of an operation whose input includes sensitive data to be stored
in such a way that it is accessible outside of secure mode.

\textbf{Network Channels} When a VM has access to sensitive data, e.g. when it
is in secure mode, it should not be able to access any other machine over the
network, with the exception of machines that are serving the sensitive data.

\textbf{Virtual Machine Access Channels} End users must access their VMs
through some network channel that connects a physical device (e.g. the user's
laptop) to the Data Capsules infrastructure.  This could be a remote terminal
connection such as SSH, or a remote desktop connection such as VNC or RDP.  In
both cases, steps must be taken to limit or eliminate channel bandwidth in order
to protect against the consequences of short and long-term compromises.

\textbf{Intramachine Covert Channels} If there are multiple VMs sharing a
single physical machine, Data Capsules must ensure that it is not possible for
one VM running in secure mode (and hence with access to sensitive data) to then
leak that data to a separate coresident VM running in maintenance mode, which
could then easily relay that data through any of the aforementioned channels.

\textbf{Intermachine Covert Channels} If there are multiple physical machines
serving VMs, there may be unexpected covert channels between them that could
allow similar data leaks from secure to maintenance VMs.  Although such attacks
are likely somewhat difficult to implement and unlikely to have very high
bandwidth, steps should be taken to minimize any such known channels to the
highest degree possible without substantially impacting performance.

The virtual machine infrastructure that underlies the Data Capsules system is
trusted and assumed to be well implemented.  While such an assumption may be
somewhat controversial, we note its use in prior work~\cite{capsules}, and also
note the existence of microkernels such as seL4 and OKL4~\cite{sel4, OKL4},
which serve as a proof of concept that it is possible to create a lightweight
hypervisor with a reasonable degree of trustworthiness.  However, the
development of such a hypervisor lies outside the scope of this paper.

\subsection{Design Overview}

Data Capsules makes heavy use of virtualization.  For each system user, there
are one or more corresponding VMs.  Multiple VMs per user may be useful in
situations where there is a large repository of data that is separated into
multiple corpora each with their own access permissions.  In this case, a user
could potentially have multiple VMs, each with access to a different corpus.
However, the handling of such an access permissions system is outside the scope
of this paper.

The fundamental element that provides the guarantees

\subsection{Maintenance Mode}

\section{Implementation}
Suspendisse potenti. Donec ornare metus sem, vel semper arcu fermentum in. Nunc
vehicula eros turpis, ut rhoncus nunc sodales pulvinar. Duis sed est interdum,
semper mi a, cursus sapien. Nulla elementum congue purus, eu faucibus nibh
congue et. Ut diam metus, euismod ac quam in, gravida dictum turpis. Vivamus
hendrerit facilisis tempor. Curabitur hendrerit orci ac libero vestibulum, sit
amet dictum enim viverra. Nulla rutrum dolor ligula, nec rutrum massa suscipit
volutpat. Aliquam id mi at velit aliquet imperdiet at nec mi. Integer in massa
nec augue dapibus ullamcorper. Aliquam nec sollicitudin elit.

\section{Discussion and Future Work}
\label{sec:Discussion}
In eu gravida ligula, sit amet tincidunt nisi. Interdum et malesuada fames ac
ante ipsum primis in faucibus.  Vestibulum venenatis non sem vitae hendrerit.
Cras accumsan vel mauris ut vestibulum. Pellentesque auctor quam ut nisl
commodo malesuada. Phasellus adipiscing placerat tortor, in convallis massa
cursus eu. Vestibulum ullamcorper lorem vel nunc dictum, elementum pretium
nulla tincidunt.
